Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-27 providence/sections/intro.tex
made the two changes from email
minor edits

%Intro
It is well-known that electronic voting systems are vulnerable to software errors and manipulation which may be undetected. Errors and/or manipulation may not always change an election outcome, but we would want to know when they do. {\em Software independent} voting systems \cite{SI-Wack,rivest2008notion} are ones where an undetected change in the software cannot lead to an undetectable change in the election outcome. The {\em evidence-based elections} \cite{evidence-based} approach requires that election outcomes be supported by strong affirmative evidence. The evidence is generated during the election and publicly examined at the end, enabling citizens to determine whether it provides strong support of the election outcome or is not sufficiently convincing. 
%by requiring not merely the use software independent systems to produce trustworthy evidence of outcome correctness; but also the examination of the evidence so that incorrect outcomes may be detected with high probability. 
One approach to evidence-based elections is to use voter-verified paper ballots, store them securely, and perform public audits---a compliance audit to determine whether the ballots were stored securely and procedures were followed; and a rigorous tabulation audit, known as a risk-limiting audit (RLA) \cite{RLA}, to determine whether the outcome is correctly computed from the stored ballots.  
%Many US states have had pilot RLA programs. Additionally, some states allow RLAs to be used towards audit requirements, and some states require RLAs before elections can be certified. 
%We propose the \Providence audit, a new approach to a particular type of RLA---the ballot polling RLA described below---and propose a new model for the work load of an election. We show that \Providence is superior to the popular ballot polling RLA \Bravo for real elections, and describe the use of our open source implementation by the Rhode Island Board of Elections for an audit of their 2021 elections. \Providence was recently integrated as an option in Arlo \cite{arlo}, the most popular election audit software. %Our open-source implementations of \Providence and our audit planning tools are likely to be useful later this year; ballot polling audits are expected to be used as pre-certification RLAs in at least one statewide contest in both Georgia and Pennsylvania for the 2022 general elections in the US.

@@

\subsection{Gaps in Prior Work and Our Contributions}
We describe relevant gaps in our knowledge of audits and then describe our contributions. 
\subsubsection{Limitations of \Minerva}
Zag\'{o}rski {\em et al.}  prove that \Minerva \cite{usenix_minerva} is risk-limiting when the number of relevant ballots drawn in each round is pre-determined before any ballots are examined. They do not address the case of a stronger adversary (such as an audit insider) who can determine the size of the next round after knowing what votes are on the ballots sampled thus far. An open question about \Minerva is whether its RLA proof holds in this case. Can the audit insider increase the audit's error probability beyond its declared risk limit? Or is there no probabilistic adversarial advantage to being able to compute next round sizes after knowing the drawn sample? We do not answer this question, and to our knowledge, it remains open.

>>>>

%Intro
It is well-known that electronic voting systems are vulnerable to software errors and manipulation which may be undetected. Errors and/or manipulation may not always change an election outcome, but we want to know when they do. {\em Software independent} voting systems \cite{SI-Wack,rivest2008notion} are ones where an undetected change in the software cannot lead to an undetectable change in the election outcome. The {\em evidence-based elections} \cite{evidence-based} approach requires that election outcomes be supported by strong affirmative evidence. The evidence is generated during the election and publicly examined at the end, enabling citizens to determine whether it provides strong support of the election outcome or is not sufficiently convincing. 
%by requiring not merely the use software independent systems to produce trustworthy evidence of outcome correctness; but also the examination of the evidence so that incorrect outcomes may be detected with high probability. 
One approach to evidence-based elections is to use voter-verified paper ballots, store them securely, and perform public audits---a compliance audit to determine whether the ballots were stored securely and procedures were followed; and a rigorous tabulation audit, known as a risk-limiting audit (RLA) \cite{RLA}, to determine whether the outcome is correctly computed from the stored ballots.  
%Many US states have had pilot RLA programs. Additionally, some states allow RLAs to be used towards audit requirements, and some states require RLAs before elections can be certified. 
%We propose the \Providence audit, a new approach to a particular type of RLA---the ballot polling RLA described below---and propose a new model for the work load of an election. We show that \Providence is superior to the popular ballot polling RLA \Bravo for real elections, and describe the use of our open source implementation by the Rhode Island Board of Elections for an audit of their 2021 elections. \Providence was recently integrated as an option in Arlo \cite{arlo}, the most popular election audit software. %Our open-source implementations of \Providence and our audit planning tools are likely to be useful later this year; ballot polling audits are expected to be used as pre-certification RLAs in at least one statewide contest in both Georgia and Pennsylvania for the 2022 general elections in the US.

@@

\subsection{Gaps in Prior Work and Our Contributions}
We describe relevant gaps in current knowledge of audits and then describe our contributions. 
\subsubsection{Limitations of \Minerva}
Zag\'{o}rski {\em et al.}  prove that \Minerva \cite{usenix_minerva} is risk-limiting when the number of relevant ballots drawn in each round is pre-determined before any ballots are examined. They do not address the case of a stronger adversary (such as an audit insider) who can determine the size of the next round after knowing what votes are on the ballots sampled thus far. An open question about \Minerva is whether its RLA proof holds in this case. Can the audit insider increase the audit's error probability beyond its declared risk limit? Or is there no probabilistic adversarial advantage to being able to compute next round sizes after knowing the drawn sample? We do not answer this question, and to our knowledge, it remains open.
